Smart Drill-Down

### 2014-11-30 TableSummarization/Paper/formal.tex
small changes

We say that rule $r_1$ {\em subsumes} rule $r_2$ if and only if $r_1$ has no more stars than $r_2$ and their values match wherever they both have non-starred values. For example, rule ($a$, $\star$) subsumes rule ($a$, $b$). Thus, if $r_1$ subsumes $r_2$, then for all tuples $t$, $t \in r_2 \Rightarrow t \in r_1$. We also write $r_1 \geq r_2$ to denote that $r_1$ subsumes $r_2$, and $r_1 > r_2$ if $r_1$ subsumes but is not equal to $r_2$ i.e. there is at least one column $c$ such that $r_2$ has a non-$\star$ value in $c$ where $r_1$ does not. If $r_1$ subsumes $r_2$, we also say that $r_1$ is a {\em sub-rule} of $r_2$ and $r_2$ is a {\em super-rule} or $r_1$.

@@

Finally, when the user clicks on a rule that has already been expanded, it reverses the expansion operation, i.e. collapses it. For example, clicking on the walmart rule in table~\ref{table:introexample3} or table~\ref{table:introexample2} would take the user back to table~\ref{table:introexample}. This operation is equivalent to a traditional
roll-up, but for smart drill downs instead of traditional drill downs.

>>>>

We say that rule $r_1$ {\em subsumes} rule $r_2$ if and only if $r_1$ has no more stars than $r_2$ and their values match wherever they both have non-starred values. For example, rule ($a$, $\star$) subsumes rule ($a$, $b$). Thus, if $r_1$ subsumes $r_2$, then for all tuples $t$, $t \in r_2 \Rightarrow t \in r_1$. If $r_1$ subsumes $r_2$, we also say that $r_1$ is a {\em sub-rule} of $r_2$ and $r_2$ is a {\em super-rule} or $r_1$.

@@

Finally, when the user clicks on a rule that has already been expanded, it reverses the expansion operation, i.e. collapses it. For example, clicking on the walmart rule in table~\ref{table:introexample3} or table~\ref{table:introexample2} would take the user back to table~\ref{table:introexample}. This operation is equivalent to a traditional
roll up, but for smart drill downs instead of traditional drill downs.

### 2014-11-30 TableSummarization/Paper/intro.tex
small changes

\section{Introduction}
Analysts often use OLAP (Online Analytical Processing) operations
such as drill down (and roll-up)~\cite{export:69578} to explore
relational databases. 
These operations are very useful for analytics and data exploration and have stood the test of time;
all commercial OLAP systems 
in existence support these operations. (Recent reports estimate the size of the OLAP market to be \$10+ Billion~\cite{gartner}.)

@@

In this paper, we present a new interaction operator 
that is an extension to a traditional 
drill down operator, aimed at providing {\em complementary}
functionality to drill down in cases where drill down is
ineffective. We call our operator {\em smart drill down}.
At a high level, smart drill down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill down.
Note that our goal is {\em not} to replace traditional 
drill down functionality, which we believe is fundamental;
instead, our goal is to provide auxiliary functionality 
which the analyst is free to use whenever they find 
traditional drill downs ineffective.

@@

To reiterate, our chief contribution in this paper is the {\em smart drill down} interaction operator,
an extension of traditional drill down, aimed at allowing analysts to zoom into the
more ``interesting'' parts of a dataset. In addition to this operator,
we develop techniques to support this operator on increasingly larger datasets:
\squishlist
\item {\em Basic Interaction:} We demonstrate that finding the optimal list of rules is {\sc NP-Hard},
and we develop an algorithm to find the approximately optimal list of rules to display when the user performs a smart drill down operation. b
\item {\em Dynamic Sample Maintenance:} To improve response time on large tables, we formalize the problem of dynamically
maintaining samples in memory to support smart drill down. 
We show that optimal identification of samples is once again {\sc NP-Hard}, and 
we develop an approximate scheme for dynamically maintaining and using multiple samples of the table in memory.
% to improve response time on large tables.
\squishend

>>>>

\section{Introduction}
Analysts often use OLAP (Online Analytical Processing) operations
such as drill down (and roll up)~\cite{export:69578} to explore
relational databases. 
These operations are very useful for analytics and data exploration and have stood the test of time;
all commercial OLAP systems 
in existence support these operations. (Recent reports estimate the size of the OLAP market to be \$10+ Billion~\cite{gartner}.)

@@

In this paper, we present a new interaction operator 
that is an extension to a traditional 
drill down operator, aimed at providing {\em complementary}
functionality to drill down in cases where drill down is
ineffective. We call our operator {\em smart drill down}.
At a high level, smart drill down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill down.
Note that our goal is {\em not} to replace traditional 
drill down functionality, which we believe is fundamental;
instead, our goal is to provide auxiliary functionality 
which analysts are free to use whenever they find 
traditional drill downs ineffective.

@@

To reiterate, our chief contribution in this paper is the {\em smart drill down} interaction operator,
an extension of traditional drill down, aimed at allowing analysts to zoom into the
more ``interesting'' parts of a dataset. In addition to this operator,
we develop techniques to support this operator on increasingly larger datasets:
\squishlist
\item {\em Basic Interaction:} We demonstrate that finding the optimal list of rules is {\sc NP-Hard},
and we develop an algorithm to find the approximately optimal list of rules to display when the user performs a smart drill down operation. 
\item {\em Dynamic Sample Maintenance:} To improve response time on large tables, we formalize the problem of dynamically
maintaining samples in memory to support smart drill down. 
We show that optimal identification of samples is once again {\sc NP-Hard}, and 
we develop an approximate scheme for dynamically maintaining and using multiple samples of the table in memory.
\squishend
